---
title: "Measuring Spatial Distribution using Activty Space"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"measuring spatial distribution using activty space"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction

The activity space is the concept of a social place that individuals visit on 
a daily basis, and the concept of an activity space itself can be thought of a 
lot on a daily basis, but it has not been dealt with largely in the study. 
However, many studies have recently been conducted in that the analysis based 
on the activity space can realistically observe the segregation and disconnection 
experienced by social members in real life compared to the existing 
residential-centered approach(Wong and Shaw, 2011; Farber et al., 2012; 
ang et al., 2012; Wang and Li, 2016). However, this activity-space-based 
research has several problems to be overcome. In order to deal with the activity
space, it is necessary to deal with data in a more complex form than the 
existing data, which causes difficulties in analysis and takes a lot of time.

The slice package was developed to make it easier to handle activity space data
in R in this flow. The slice package can find out what area people are located 
at a specific time based on people's activity space, based on each travel record,
and has a function that makes it easier to handle such travel records.

In this Vignette, we will use the 2016 Korea Transport Database of South 
Korea to deal with how and where people are distributed in each time zone 
through slice package.

```{r setup, message = FALSE}
library(devtools)
load_all()
```

## Classes

Before actually starting, I will explain the two classes included in the package 
with data. The slice package has two classes, the names of these two classes are 
ASpace and ASpaces, respectively. First, let's proceed with the explanation 
while looking at the data.

```{r}
data("Krtrdata")
```
```{r}
class(korea2016)
##ASpaces class
korea2016@data[[1]]
korea2016@attr
##Not run
#korea2016@sp 
```
First is the ASpaces class. The ASpaces class has a total of three slots, 
each of which is 'data', 'attr', and 'sp'.

* The slot 'data' contains activity space information for us to analyze, 
and each one is entered into the list inside the data slot.

* The slot 'attr' is the metadata of the ASpaces class, and contains the 
time when the data was collected or the name of the data.

* Finally, the slot 'sp' contains SpatialPolygon or SpatialPoint that contains the 
spatial extent of the activity space.

    Note that the space unit or spatial range of the data inside the sp 
    slot must match the data inside the data slot.

```{r}
class(korea2016@data[[1]])
##ASpace class
korea2016@data[[1]]@info
korea2016@data[[1]]@trip
```
Next is the ASpace class. Unlike the ASpaces class, ASpace has one active space 
and demographic data, and has a total of two slots. Each slot is Info and Trip.

* The slot 'info' contains demographic and socioeconomic variables
of the respondent as a list object.

* The slot 'trip' contains information on trips made by the survey respondent.

In other words, if you briefly describe these two classes, 
you can say that the ASpace class is a class that has data for each person, 
and ASpaces is a class that has multiple data as its name suggests.

When looking at the data inside ASpace, the data starts with each individual 
number and has demographic characteristics such as gender and income level in 
the residential area, and inside the trip, it is possible to check the 
characteristcs associated with travel.

    Note that we have looked at the data, let's see how we can actually 
    analyze the activity space based on this class.

## Measuring spatial distribution

First of all, in the simplest way, it will be possible to measure whether the 
degree of distribution of people can vary by time zone. As the name suggests, 
the slice function slices consecutive data in time and allows you to see 
a section of time.

The slice function can be easily used as follows.

* `slice(x, at)`

In this syntax, enter the ASpaces class for x and enter your desired time for at. 
Like this, if you want to check the population distribution at 2 p.m. of the 
data you have, the function can be entered as follows.

* `slice(korea2016, 1400)`

Of course, you can simply input this, but it is expected that the operation time 
will take a long time due to the size of the data, so let's make it possible to 
perform faster operation by entering an additional statement.

It was adjusted to enable parallelized operation through the mc argument, and 
the function was controlled to operate in a total of 4 cores through the 'core' 
argument. The result appears as follows.

```{r}
library(parallel)
all1400 <- slice(korea2016, 1400, silent = TRUE, mc = TRUE, core = 4)
head(all1400)
nrow(all1400)
```

When you check the result, you can see that the format has changed compared to 
the previous one, and also that several variables have been added. In other 
words, a result in the form of data.frame indicating the purpose of which 
individuals with demographic characteristics on the left arrived at the location
by means of transportation for what purpose was derived. And through the last 
on.move variable, you can also check whether the person is currently moving or 
is active in the area.

However, since the resulting data frame contains too much data (108022), 
it is difficult to know which regions are distributed more and which regions 
are less distributed. Therefore, we will refine the resulting data and find out 
how much it is distributed by region through the slice2df function.

The simple usage of slice2df function is as follows.

* `slice2df(x, var1)`

In this syntax, the data frame that is the result of slice is input in x, and 
the location of data.frame is input in var.

```{r}
head(slice2df(all1400, "location"))
```

Like this, you can check how many people are active by region at that time. 
slice2df also uses an additional variable You can check the distribution of the 
population by region in more detail.

```{r}
result1 <- slice2df(all1400, "location", "sex")
head(slice2df(all1400, "location", "sex"))
```

Of course, you can check the results more easily than before in this way, 
but the table is still too long to check the results at once.
It is true that it is still difficult. From now on, we will visualize with the 
data of sp class inside ASpaces.

## Visualization

The result of slice can be visualized on the premise that the space unit of sp 
inside ASpaces is the same as the unit of activity space. 
First, merge the result and sp data for visualization.

```{r}
korea2016@sp@data <- merge(korea2016@sp@data, 
                           result1, by.x = "adm_cd", by.y = "Area")  
head(korea2016@sp@data)
```

Since the number of population counted by region has been well entered into the 
spatial data, a simple visualization can now proceed.

The code for visualization is as follows.

```{r, out.width = "70%", fig.align='center'}
library(RColorBrewer)
library(classInt)
## Specify par so that three maps fit on one screen
par(mar = c(1, 1, 1, 1))
par(mai=c(1, 0, 1, 0))
par(mfrow = c(1, 3))

## Visualization for Male distribution
my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 7], 5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Male", border = F)

## Visualization for Female distribution
my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 8], 5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Female", border = F)

## Visualization for total population distribution
my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 7] + korea2016@sp@data[, 8], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Both", border = F)
```

When checking the visualization results, it was found that there was no 
significant difference in the distribution between men and women at 2:00 pm.
Of course, these results may have a large influence on working hours due to the 
specificity of time. If so, what would be the result of different times?

```{r}
library(parallel)
## Set the time to 8:00 am and 20:00 pm
all800 <- slice(korea2016, 800, silent = TRUE, mc = TRUE, core = 4)
all2000 <- slice(korea2016, 2000, silent = TRUE, mc = TRUE, core = 4)

## refining results
result2 <- slice2df(all800, "location", "sex")
result3 <- slice2df(all2000, "location", "sex")

## merging results to sp slot
korea2016@sp@data <- merge(korea2016@sp@data, 
                           result2, by.x = "adm_cd", by.y = "Area")  
korea2016@sp@data <- merge(korea2016@sp@data, 
                           result3, by.x = "adm_cd", by.y = "Area") 

head(korea2016@sp@data)
```

```{r, out.width = "70%", fig.align='center'}
par(mar = c(1, 1, 1, 1))
par(mai=c(1, 0, 1, 0))
par(mfrow = c(1, 3))

## Visualization of 8 AM results


my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 9], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Male", border = F)

my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 10], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Female", border = F)

my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 9] + korea2016@sp@data[, 10], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Both", border = F)

```
```{r, out.width = "70%", , fig.align='center'}
par(mar = c(1, 1, 1, 1))
par(mai=c(1, 0, 1, 0))
par(mfrow = c(1, 3))
## Visualization of 8 PM results
my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 11], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Male", border = F)


my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 12], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Female", border = F)

my_colors <- brewer.pal(5, "Reds")
class_of_freq <- classIntervals(korea2016@sp@data[, 11] + korea2016@sp@data[, 12], 
                                5, style = "jenks")
colors <- findColours(class_of_freq, my_colors)
plot(korea2016@sp, col = colors, main = "Both", border = F)

```

In this way, you can see how it changes over time. This can be confirmed as a 
result of spatially differentiated residences and jobs in Seoul, Korea. However,
it was confirmed that the difference between women and men still did not appear 
noticeably. It can be interpreted that the spatial distribution of men and women 
is not very different in terms of activity space.






























































